### 2016-02-29 ch05-initvals/initial-values.tex
Update flowgraph

\subsection{Initial Estimates Procedure}\label{sec:init:procedures}
\begin{figure}[p]
  \centering
  \includegraphics[width=\columnwidth]{\thisDir/fig/flowgraph}
  \caption[Flow chart of different initialization procedures.]{Flow chart depicting the different estimation procedures, from left to right: \circledNum{1} an approach using the true model as initial estimate; \circledNum{2} an existing approach using \gls{BTLS} and \gls{GTLS} starting values, and the novel initialization strategies outlined in this chapter (\circledNum{3}, \circledNum{4}) that make use of smoothers to generate improved starting values for the non-convext optimization problem.
  The flow of non-parametric data is depicted by full arrows, with the \gls{FRF} data marked by asterisks. Parametric models are indicated by dashed, unfilled arrows.} 
  \label{fig:flowgraph}
\end{figure}

>>>>

\subsection{Initial Estimates Procedure}\label{sec:init:procedures}
\begin{figure}[p]
  \centering
  \includegraphics[width=\columnwidth]{\thisDir/fig/flowgraph}
  \caption[Flow chart of different initialization procedures.]{Flow chart depicting the different estimation procedures, from left to right: \circledNum{1} an approach using the true model as initial estimate; \circledNum{2} an existing approach using \gls{BTLS} and \gls{GTLS} starting values, and the novel initialization strategies outlined in this chapter (\circledNum{3}, \circledNum{4}) that make use of smoothers to generate improved starting values for the non-convex optimization problem.
  The flow of non-parametric data is depicted by full arrows, with the \gls{FRF} data marked by asterisks. Parametric models are indicated by dashed, unfilled arrows.} 
  \label{fig:flowgraph}
\end{figure}
